%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior engineer} % Job title
    {University of Oslo}
    {Oslo, Norway} % Location
    {Aug. 2020 - Jan 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Work on various infrastructure components:}
          \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
          \item \url{https://github.com/unioslo/mreg}
          \item \url{https://github.com/unioslo/mreg-cli}
          \item \url{https://github.com/unioslo/zabbix-cli}
          \item \url{https://github.com/unioslo/zabbix-auto-config}
          \end{itemize}
        \item {Create continuous integrations with GitHub Actions.}
        \item {Co-maintain internal systems:}
          \begin{itemize}[leftmargin=2ex, nosep, noitemsep]
          \item {Zabbix}
          \item {mreg}
          \item {Harbor Docker registry}
          \end{itemize}
        \item {End user support.}
      \end{cvitems}
    }



%---------------------------------------------------------
  \cventry
    {Co-founder} % Job title
    {Devup SA}
    {Trondheim, Norway} % Location
    {Feb. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Consulting work for various clients.}
        \item {Written REST APIs in Scheme, Python, Java.}
        \item {Deploy Docker containers in Azure App Service.}
        \item {Deploy React app with Azure CDN and blob storage.}
        \item {Create CI/CD pipelines in Azure DevOps.}
        \item {Unix maintainance tasks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {ITsjefen AS}
    {Trondheim, Norway} % Location
    {May. 2017 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained various customer and internal servers.}
        \item {Deployed Ganeti cluster for internal use.}
        \item {Deployed Elasticsearch cluster for log centralization.}
        \item {Configured PXE boot infrastructure for unattended OS deployment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cloud Administrator} % Job title
    {Cloud Infrastructure for Microbial Bioinformatics (CLIMB, University of Warwick)}
    {Coventry, United Kingdom} % Location
    {Dec. 2014 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, deploy and maintain 4x 1.6PB Ceph storage clusters.}
        \item {With replicated Amazon S3 compatible API across sites.}
        \item {Configured and maintained 960-core Openstack cluster.}
        \item {Maintained 500TB GPFS/Spectrum Scale FC cluster.}
        \item {Ditched Vyatta for OpenBSD on redundant 40Gbit firewalls.}
        \item {Everything managed through xCAT and SaltStack.}
        \item {Maintained Brocade Ethernet and Mellanox Infiniband fabrics.}
        \item {Packaged bioinformatics software for GNU~Guix.}
        \item {Help with troubleshooting and training at sister sites.}
        \item {End user support and training.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {Sportradar AS} % Organization
    {Trondheim, Norway} % Location
    {Nov. 2010 - Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated a large and complex ad-hoc infrastructure to managed Ganeti VMs.}
        \item {Introduced Puppet for configuration management on said fleet.}
        \item {Maintained several highly available clusters (Ceph, MySQL, Varnish, web).}
        \item {Capacity planning for high uptime and more than 100k HTTP req/s.}
        \item {Wrote numerous data collectors and other scripts for monitoring systems and similar.}
        \item {Maintained many internal applications (Gitlab, Zabbix, Jenkins, and others).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Job title
    {Norwegian Infrastructure for the Exploration of Syntax and Semantics (INESS)} % Organization
    {Bergen, Norway} % Location
    {Jun. 2010 - Feb. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Procured and deployed Lustre storage, oVirt platform, and OpenBSD firewalls.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Part-Time System Administrator} % Job title
    {Uni Digital} % Organization
    {Bergen, Norway} % Location
    {Apr. 2009 - Aug. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained LAMP stack, Zope, and various in-house applications.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Coordinator} % Job title
    {Fabricom Suez} % Organization
    {Stavanger, Norway} % Location
    {Sep. 2007 - Apr. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Support and maintenance of branch office (Active Directory, workstations, network).}
        \item {Optimizations of central firewall ruleset.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IKT-driftsoperatør} % Job title
    {Troms Fylkeskommune (Bardufoss and Høgtun VGS)} % Organization
    {Bardufoss, Norway} % Location
    {Aug. 2004 - Aug. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Automated provisioning of workstations with RIS and VBscript.}
        \item {Support and maintain large Active Directory with OS X and Linux clients.}
        \item {Participated in many network and hardware rollouts.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
